Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-09 main.tex
add conclusion

\section{Conclusions}

>>>>

\section{Conclusions}
In this work, we utilize the \wvtwo \fe as a replacement for traditional feature extraction methods in a \gls{CTC} \gls{ASR} model on LibriSpeech.
It shows competitive performance and outperforms an alternative neural \fe, namely the \gls{SC} features, slightly.
We demonstrate that its width is more responsible for its capabilities that its depth and show that pre-training the \fe only is not beneficial.
Finally, we analyze the learned filters and highlight the differences between both neural \fes.
In particular, it is shown that the \gls{SC} \fe's learned bandpass filters encode the valuable information for the \gls{ASR} system while the remaining wideband filter information is largely ignored.
